A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
intro analysis para

Our research contributions in this paper can be summarized as follows.
\begin{itemize}
	\item Automation of the installation, configuration, and dataset conversion to ensure the experiments execute in the same manner. Essentially, we provide a ``level playing field'' for graph algorithms.
	\item Comparison of algorithm runtime and scalability using a variety of data sets.
	\item Comparison of our framework with the Graphalytics \cite{Capota:2015:Graphalytics} project.
	\item Inspection of the source code of the surveyed parallel graph processing systems to ensure the same phases of execution are measured across differing execution and programming paradigms
	\item Provision of a experimental framework distinguishing between the data structure generation and algorithm execution phases of each system.
	\item Analysis of energy consumption during the algorithm execution phase.
\end{itemize}

@@

\section{Experimental Setup}
We refer to a graphs's \emph{scale} when describing the size of the graph. Specifically, a graph with scale $S$ has $2^S$ vertices. The datasets are described further in Sect.~\ref{sec:datasets}. We measure strong scaling and speedup by varying the number of threads from one to the total number of threads on the reasearch machine, 72.

@@

We plot many of the results as box plots with an implied 32 datapoints per box.

\subsection{Machine Specifications}
Table~\ref{tab:specs} shows the specifications of the research computer.

@@

This report explores four shared memory parallel graph processing platforms. The first three are so-called ``reference implementations'' while the remaining two are included because of their performance and popularity. Our target is shared memory CPU processing. Other popular libraries such as the Parallel Boost Graph Library \cite{Gregor:2005:PBGL} are not considered here because the authors do not provide reference implementations. The systems are:

\begin{enumerate}
	\item The Graph500\footnote{We used the most recent version from \url{https://github.com/graph500/graph500}, most similar to release 2.1.4.} \cite{Murphy:2010:Graph500}
	\item The Graph Algorithm Platform (GAP) Benchmark Suite \cite{Beamer:2015:GAPBench}
	\item GraphBIG \cite{Nai:2015:Graphbig}
	\item GraphMat \cite{Sundaram:2015:GraphMat}
	\item PowerGraph \cite{Gonzalez:2012:Powergraph}
\end{enumerate}

\subsection{Algorithms}

We consider three algorithms: Breadth First Search (BFS), Single Source Shortest Paths (SSSP), and PageRank, though not all algorithms are implemented on all systems.

@@

>>>>

Our research contributions in this paper can be summarized as follows.
\begin{itemize}
	\item Automation of the installation, configuration, and dataset conversion to ensure the experiments execute in the same manner. Essentially, we provide a ``level playing field'' for graph algorithms.
	\item Comparison of algorithm runtime and scalability using several data sets.
	\item Comparison of our framework with the Graphalytics \cite{Capota:2015:Graphalytics} project.
	% BN: I think the bullet below is a bit too low-level for this summary, moving to later section.
	%\item Inspection of the source code of the surveyed parallel graph processing systems to ensure the same phases of execution are measured across differing execution and programming paradigms.
	\item An experimental framework distinguishing between the data structure generation and algorithm execution phases of each system.
	\item Analysis of energy consumption during the algorithm execution phase.
\end{itemize}

@@

\section{Experimental Setup}
We refer to a graphs's \emph{scale} when describing the size of the graph. Specifically, a graph with scale $S$ has $2^S$ vertices. The datasets are described further in Sect.~\ref{sec:datasets}. We measure strong scaling and speedup by varying the number of threads from one to the total number of threads on our server, 72.

@@

We plot many of the results as box plots with an implied 32 data points per box.

\subsection{Machine Specifications}
Table~\ref{tab:specs} shows the specifications of the server on which we performed all experiments.

@@

This study explores four shared memory parallel graph processing platforms. The first three are so-called ``reference implementations'' while the remaining two are included because of their performance and popularity. Our target is shared memory CPU processing. Other popular libraries such as the Parallel Boost Graph Library \cite{Gregor:2005:PBGL} are not considered here because the authors do not provide reference implementations. We consider the following systems.
\begin{itemize}
	\item The Graph500\footnote{We used the most recent version from \url{https://github.com/graph500/graph500}, most similar to release 2.1.4.} \cite{Murphy:2010:Graph500}, a set of large-scale graph benchmarks.
	\item The Graph Algorithm Platform (GAP) Benchmark Suite \cite{Beamer:2015:GAPBench}.
	\item GraphBIG \cite{Nai:2015:Graphbig} benchmark suite.
	\item GraphMat \cite{Sundaram:2015:GraphMat}, a high-performance graph library.
	\item PowerGraph \cite{Gonzalez:2012:Powergraph}, a framework for distributed graph-parallel computation on natural graphs.
\end{itemize}

Our approach is not specific or limited to these graph packages and can be extended to others with relatively modest effort (building each package and if necessary, instrumenting the different phases of the computation).

\subsection{Algorithms}\label{sec:algs}

We consider three algorithms: Breadth First Search (BFS), Single Source Shortest Paths (SSSP), and PageRank, though not all algorithms are implemented on all systems. We inspected the source code of the surveyed parallel graph processing systems to ensure the same phases of execution are measured across differing execution and programming paradigms.

@@

We analyze the performance of the algorithms described in Sec.~\ref{sec:algs} in terms of execution time, scalability over multiple threads, and power and energy consumption.
